Decomposing labelled proof theory for intuitionistic modal logic

### 2019-08-22 caleidoscope/caleidoscope.tex
small modif

	The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
	%
	Starting with a set $\mathcal{A}$ of atomic propositions, denoted $a$, modal formulas are constructed from the grammar:
	%
	$$
	A \coloncolonequals
	a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
	$$
	%
	%We might sometimes write $\NOT A$ to mean $A \IMP \BOT$.

%Obtaining the intuitionistic variant of K is more involved than the classical variant. 
%%
%Lacking De Morgan duality, there are several variants of k that are classically but not intuitionistically
%equivalent. 
%%
%Five axioms have been considered as primitives in the literature. 
%

>>>>

	The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
	%
	Starting with a set $\mathcal{A}$ of atomic propositions, denoted $a$, modal formulas are constructed from the grammar:
	%
	$$
	A \coloncolonequals
	a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
	$$
	%
	We might sometimes write $\NOT A$ to mean $A \IMP \BOT$.

Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
%%
Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent. Five axioms have been considered as primitives in the literature. 
%
